{\bf Topology, Geometry and Morphology of the Dark Matter Web}

### 2018-07-24 Draft/Chapter6/concl.tex
final changes

The full dynamical state of cold dark matter can be described as a three-dimensional sub-manifold
in six-dimensional phase space - the dark matter sheet. In our study we use a Lagrangian sub-manifold ${\bf x} = {\bf x}({\bf q},t)$ 
(where {\bf x} and {\bf q} are co-moving Eulerian and Lagrangian coordinates respectively), which 
is dynamically  equivalent to the dark matter sheet but is more convenient for numerical analysis. Projecting the Lagrangian sub-manifold at each point in the configuration space defines the multistream field  $n_{str}(\mathbf{x}, z)$. This integer-valued field is equivalent to counting the number of foldings in the sub-manifold and we numerically calculate by a Lagrangian tessellation scheme. The resulting multistream field is positively correlated with matter density, and supplements our knowledge of spatial clustering. It is a fundamental feature of collisionless dark matter structures, and is of great importance in understanding the dynamical collapse of

@@

The multistream web represents a nested structure, consisting of layers with increasing number of streams.

>>>>

The full dynamical state of cold dark matter can be described as a three-dimensional sub-manifold
in six-dimensional phase space - the dark matter sheet. In our study we use a Lagrangian sub-manifold ${\bf x} = {\bf x}({\bf q},t)$ 
(where {\bf x} and {\bf q} are co-moving Eulerian and Lagrangian coordinates respectively), which 
is dynamically equivalent to the dark matter sheet but is more convenient for numerical analysis. Projecting the Lagrangian sub-manifold at each point in the configuration space defines the multistream field  $n_{str}(\mathbf{x}, z)$. This integer-valued field is equivalent to counting the number of foldings in the sub-manifold and we numerically calculate by a Lagrangian tessellation scheme. The resulting multistream field is positively correlated with matter density, and supplements our knowledge of spatial clustering. It is a fundamental feature of collisionless dark matter structures, and is of great importance in understanding the nonlinear gravitational collapse.

@@

\hl{The multistream web represents a nested structure, consisting of layers with increasing number of streams.}
